Type cones of $\b{g}$-vector fans

### 2019-02-28 thirdPaper/draft/typeConeAssociahedra.tex
minor modifs
objects presented

\begin{corollary}
Assume that~$\ind(\cat)$ is finite.
Let~$X\infl E\defl Y\dashrightarrow$ be any extriangle.
Then the element~$x=[X]+[Y]-[E]$ of the kernel of~$\b g$ is a non-negative linear combination of the~$\ell_A$, with~$A\in\ind(\cat)\ssm \add(\susp T)$.
\end{corollary}

@@

@@

>>>>

\begin{corollary}\label{corollary::meshes positively generate extricats}
Assume that~$\ind(\cat)$ is finite.
Let~$X\infl E\defl Y\dashrightarrow$ be any extriangle.
Then the element~$x=[X]+[Y]-[E]$ of the kernel of~$\b g$ is a non-negative linear combination of the~$\ell_A$, with~$A\in\ind(\cat)\ssm \add(\susp T)$.
\end{corollary}

@@

\begin{proof}[Proof of Theorem~\ref{theorem::extricats}]\yann{PG: Est-ce que cela te semble suffisant, ou veux-tu que j'ajoute des d\'etails ? }
 The proof is know similar to the proof of Theorem~\ref{theo::relations-g-vecteurs}, by using Proposition~\ref{prop::KRextricat} instead of Proposition~\ref{prop::functor-F}, Proposition~\ref{prop::index iso extricat} instead of Corollary~\ref{coro::grothendieck-g-vectors}, and the fact that~$\tc$ is made of projective objects instead of Lemma~\ref{lemm::almost-split}.
\end{proof}

\begin{proof}[Proof of Corollary~\ref{corollary::meshes positively generate extricats}]
\yann{TO DO}
\end{proof}

@@

We know describe a setup satisfying the assumptions of Section~\ref{sect::setting} that, at the same time, subsumes all examples given so far, while being easily checked in practice.\yann{A reformuler...}

Let~$(\ec,\mathbb{E},\mathfrak{s})$ be an extriangulated category (for example, a small exact category or a triangulated category), and let~$\tc$ be an essentially small \yann{Cette hypoth\`ese n'appara\^it pas dans [HLN], mais me semble n\'ecessaire...} subcategory of~$\ec$.

For any~$X,Y\in\ec$, let~$\mathbb{E}_\tc(X,Y)$ be the subset of~$\mathbb{E}(X,Y)$ consisting of those~$\delta$ that satisfy~$f^\ast\delta = 0$, for any~$T\in\tc$ and any~$T\xrightarrow{f}X$.
It is easily seen that~$\mathbb{E}_\tc$ is an additive subfunctor of~$\mathbb{E}$.
Consider $(\ec,\mathbb{E}_\tc,\mathfrak{s}_\tc)$ endowed with the resctriction of the additive realisation~$\mathfrak{s}$.
Since the deflations in~$(\ec,\mathbb{E}_\tc,\mathfrak{s}_\tc)$ are precisely the deflations in~$(\ec,\mathbb{E},\mathfrak{s})$ that are~$\tc$-epic, they are closed under composition.
We can thus apply~\cite[Proposition 3.14]{HerschendLiuNakaoka} to obtain that~$(\ec,\mathbb{E}_\tc,\mathfrak{s}_\tc)$ is an extriangulated category.
With that relative structure, the objects in~$\tc$ become projective.
Define~$\cat$ to be the full subcategory of~$\ec$ whose objects~$X$ admit an~$\mathfrak{s}_\tc$-conflation~$T_1\infl T_0\defl X$.

\begin{lemma}
 The full subcategory~$\cat$ is extension-closed in~$(\ec,\mathbb{E}_\tc,\mathfrak{s}_\tc)$, and thus inherits an extriangulated structure.
\end{lemma}

\begin{proof}
 This follows from the proof of Lemma~\ref{lemma::index kzero extricat}.
\end{proof}

\begin{proposition}
